Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-03-24 paper/introduction.tex
fixed minor typos

The \emph{Software Analysis Workbench} (\saw) is a formal verification tool to prove equivalence between \sawcore\ models. \sawcore\ models are defined in the \cryptol\ functional language or extracted from C or Java with \emph{symbolic execution}.
\cryptol\ itself is designed to specify cryptographic primitives at the bit level.
\saw\ has been shown capable in proving implementations of cryptographic primitives equivalent to hardware and software implementations \cite{crypt-hi,hard-soft,design-verif}.
Recent work emphasizes not just the utility of \saw, but the importance of modular decomposition of cryptographic primitives in their definition as that decomposition lends itself to efficient verification in \saw \cite{nfm-us}.

>>>>

The \emph{Software Analysis Workbench} (\saw) is a formal verification tool to prove equivalence between \sawcore\ models. \sawcore\ models are defined in the \cryptol\ functional language or extracted from C or Java with \emph{symbolic execution}.
\cryptol\ itself is designed to specify cryptographic primitives at the bit level.
\saw\ has been shown capable in proving implementations of cryptographic primitives equivalent to hardware and software implementations \cite{crypt-hi,hard-soft,design-verif}.
Recent work emphasizes not just the utility of \saw, but the importance of modular decomposition of cryptographic primitives in their definition as that decomposition lends itself to efficient verification in \saw\ \cite{nfm-us}.

### 2022-03-24 paper/related.tex
Fix grammar errors
fixed minor typos

\cryptol\ has been used to formally verify different implementations of the same cryptographic algorithm in the past.
As a demonstration of \cryptol, Lewis \emph{et al} provided portions of the \emph{Advanced Encryption Standard} (AES) implemented in the language \cite{crypt-hi}.
The language has also been used to verify equivalence between Skein Hash algorithm implementations \cite{hard-soft}.
\cryptol\ is not limited to hardware, as Browning and Weaver \cite{design-verif} have shown that the language can be tuned to provide an abstraction of hardware.
They later provided a proof of equivalence between the FIPS AES specification and various optimized \cryptol\ implementations.
For certain tables, they initially demonstrated equivalence through mathematical principles.
These tables were also proven equivalent to less time-intensive statically defined tables used for the rest of their proofs.
As the OpenSSL implementation was highly optimized with similar static values, this paper mirrored the method Browning and Weaver outlined.
The language was also used to verify equivalence between the specification and hardware of the Verilog RTL's pseudorandom number generator \cite{pseudorandom}.

Decker et al's verification of OpenSSL's \shaTwo\ 256 bit digest implementation served as a direct predecessor to this work \cite{nfm-us}.
While \shaTwo\ is also part of the \nist\ Secure Hash Algorithms, its internal structure differs vastly from the more complex and resistant \shaThree.
The \shaTwo\ proof, in turn, expanded the methodology by which Amazon's s2n HMAC was verified \cite{chudnov,s2n-blog}.
While \shaThree\ is not implemented in s2n, the HMAC verification provided utilized both a high-level and low-level \cryptol\ specification in a similar manner to this work.
Both works compared equivalent C and \cryptol\ specification through \saw.
Decker's work is inspired by the \openssl verification of HMAC from Beringer \cite{beringer}.

>>>>

\cryptol\ has been used to formally verify different implementations of the same cryptographic algorithm in the past.
As a demonstration of \cryptol, Lewis \emph{et al} provided portions of the \emph{Advanced Encryption Standard} (AES) implemented in the language \cite{crypt-hi}.
The language has also been used to verify equivalence between Skein Hash algorithm implementations \cite{hard-soft}.
\cryptol\ is not limited to software, as Browning and Weaver \cite{design-verif} have shown that the language can be tuned to provide an abstraction of hardware.
They later provided a proof of equivalence between the FIPS AES specification and various optimized \cryptol\ implementations.
For certain tables, they initially demonstrated equivalence through mathematical principles.
These tables were also proven equivalent to less time-intensive statically defined tables used for the rest of their proofs.
As the OpenSSL implementation was highly optimized with similar static values, this paper mirrored the method Browning and Weaver outlined.
The language was also used to verify equivalence between the specification and hardware of the Verilog RTL's pseudorandom number generator \cite{pseudorandom}.

Decker et al's verification of OpenSSL's \shaTwo\ 256 bit digest implementation served as a direct predecessor to this work \cite{nfm-us}.
While \shaTwo\ is also part of the \nist\ Secure Hash Algorithms, its internal structure differs vastly from the more complex and resistant \shaThree.
The \shaTwo\ proof, in turn, expanded the methodology by which Amazon's s2n HMAC was verified \cite{chudnov,s2n-blog}.
While \shaThree\ is not implemented in s2n, the HMAC verification provided utilized both a high-level and low-level \cryptol\ specification in a similar manner to this work.
Both works compared equivalent C and \cryptol\ specification through \saw.
Decker's work is inspired by the \openssl\ verification of HMAC from Beringer \cite{beringer}.

### 2022-03-24 paper/saw.tex
fixed minor typos

\cryptol\ is a domain specific functional language for describing cryptographic primitives, such as algorithms to compute digests, at the bit-level.
Cryptographic primitives are the building blocks for complex cryptographic protocols, such as the \emph{Secure Sockets Layer} (SSL) and \emph{Transport Layer Security} (TLS) protocols, that provide a broad range of security guarantees.
\cryptol\ is executable, being able to run test vectors to validate specifications, and more importantly, it compiles directly to \sawcore\ which is the language for formal models in \saw.

>>>>

\cryptol\ is a domain specific functional language for describing cryptographic primitives, such as algorithms to compute digests, at the bit-level.
Cryptographic primitives are the building blocks for complex cryptographic protocols, such as the \emph{Secure Sockets Layer} (SSL) and \emph{Transport Layer Security} (TLS) protocols, that provide a broad range of security guarantees.
\cryptol\ is executable, being able to run test vectors to validate specifications, and more importantly, it compiles directly to \sawcore, which is the language for formal models in \saw.
